---
title: "Assignment 3 - ICR"
author: "Sara Murphy"
date: "2026-04-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 3 - Intercoder Reliability

# Load Data

```{r}
library(readxl)
library(here)
library(irr)

df <- read_excel(here("assignment3", "data", "llm_all_predictions.xlsx"))


```


# Use Fleiss' Kappa
Average Kappa is 0.588 which is believed to be a "moderate" level of correlation across the 4 approaches (human, zero shot, memory and memory feedback). P value is approximately 0, meaning the correlations are not due to random chance. 

```{r }
library(irr)

# Select only coder columns
ratings <- df[, c("class", "zero_shot_pred", "memory_pred", "memory_feedback_pred")]

# Fleiss' Kappa
kappa2 <- kappam.fleiss(ratings)

print(kappa2)
```

## Comparing Human to Each LLM Model

Largest Kappa is comparing human to zero shot (0.44)
Next highest Kappa is comparing human to memory feedback (0.428)
Lowest Kappa is copmaring human to memory (0.409)

This suggests that LLMS are internally consistent but are weaker when compared directly against the human coding. 

```{r}
kappa2(df[, c("class", "zero_shot_pred")])
kappa2(df[, c("class", "memory_pred")])
kappa2(df[, c("class", "memory_feedback_pred")])
```
# Comparing LLMS on reliability

As shown below, there is moderately strong reliability when looking at pairwise comparisons of the LLM models.

The highest Kappa is between memory and memory feedback (0.821).
The next highest Kappa is between zero shot and memory (0.744).
The lowest Kappa is between zero shot and memory feedback (0.72).

```{r}
kappa2(df[, c("zero_shot_pred", "memory_pred")])
kappa2(df[, c("zero_shot_pred", "memory_feedback_pred")])
kappa2(df[, c("memory_pred", "memory_feedback_pred")])

```

